\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2019-09-14 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Changed the hierarchical structure in figure 1
made mervyns changes

Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem. In this setting, we show that reconciled forecasts will have a number of attractive properties when they are obtained via projections. We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that regression based-methods themselves are indeed projections. As such, this paper is in part a review of existing results cast in a new light. In addition, we also propose three major and novel results.

First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints. As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling. Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function. We believe that this link is lacking in previous work that attempts to establish similar results, in particular \citet{VanErven2015a} and \citet{WicEtAl2019}. Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity. Third, we revisit the issue of bias. We prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased. A natural question that arises is what to do in the case of biased reconciled forecasts. Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation. This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.

The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom-level series. Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in~\ref{sec:BiasInRecon}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future of research in forecast reconciliation.

@@

\begin{figure}[!hbt]
  \begin{center}
    \leaf{AA} \leaf{AB}
    \branch{2}{A}
    \leaf{BA} \leaf{BB}
    \branch{2}{B}
    \branch{2}{Tot}
    \qobitree
  \end{center}
  \caption{An example of a two level hierarchical structure.}\label{fig:basichier}
\end{figure}

To clarify these concepts, consider the example of the hierarchy in Figure~\ref{fig:basichier}. For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
\[
  \bm{S} = \begin{pmatrix}
    1 & 1 & 1 & 1 \\
    1 & 1 & 0 & 0 \\
    0 & 0 & 1 & 1 \\
    & \multicolumn{2}{c}{\bm{I}_4} &
  \end{pmatrix},
\]
where $\bm{I}_4$ is the $4\times 4$ identity matrix.

While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series. In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics: the first is that they are multivariate, the second is that they adhere to linear constraints.

@@

\begin{definition}[Coherent subspace]\label{def:cohspace}
   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
\end{definition}

To further illustrate, Figure~\ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$. The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space; i.e. $m=2$ and $n=3$. It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$; i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$. In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$. However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$. However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

@@

Although pre-multiplying base forecasts by $\bm{S}\bm{G}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{S}\bm{G}$ has the specific structure of a \emph{projection} matrix onto $\mathfrak{s}$. In general a projection matrix is defined via its idempotence property, i.e. $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$. However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}. In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{S}\bm{G}\bm{v}=\bm{v}$.

@@

Consider the Euclidean distance between the target and a forecast. This is equivalent to the root of the sum of squared forecast errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

@@

However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy. In particular, this measure is the root of the sum of squared forecast errors of \emph{all} variables in the hierarchy. Consequently, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy. Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT\@. It is to oblique projections that we now turn our attention.

@@

One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of \emph{all} variables in the hierarchy. A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally. For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series. Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating squared errors. An even more sophisticated understanding may take the correlation between series into account. All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix. Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.

@@

Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality). In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality. The proof of \citet{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees. The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$. As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is only true with respect to a loss function that depends on $\bm{W}$. If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts. This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.

@@

\begin{figure}[!p]
  \centering
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
      \caption{}
  \end{subfigure}
  \caption{A schematic representing orthogonal and oblique reconciliations. The orange points in (a) represent in-sample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in (b) indicate potential base forecasts while the blue dot ${\hat{\bm y}}$ represents one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. (c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.}\label{fig:OthogonalVSOblique_projection}
\end{figure}

@@

Before turning our attention to the issue of bias itself it is important to state a sensible property that any reconciliation method should have. That is if base forecasts are already coherent then reconciliation should not change the forecasts. As stated in Section~\ref{sec:Reconciliation}, this property holds only when $\bm{S}\bm{G}$ is a projection matrix. As a corollary, reconciling using an arbitrary $\bm{G}$, may in fact change an already coherent forecast.

@@

The above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$, $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$. In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.

@@

Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{S}\bm{G}\bm{S}=\bm{S}$ or alternatively that $\bm{G}\bm{S}=\bm{I}$. Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in Appendix A for a proof). However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{G}\bm{S}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner. However, equipped with a geometric understanding of the problem, we would advise against this approach. The constraint $\bm{G}\bm{S}=\bm{I}$ is not just about bias. Dropping the constraint compromises all of the attractive properties of projections. It also opens the door to reconciliation methods that change already coherent base forecasts, which suggests an increase in the variability of the forecasts. This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.

>>>>

Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem. In this setting, we show that reconciled forecasts will have a number of attractive properties when they are obtained via projections. We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that regression based-methods themselves are indeed projections. As such, this paper is in part a review of existing results cast in a new light. In addition, we also derive three major and novel results.

First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints. As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling. Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function. We believe that this link is lacking in previous work that attempts to establish similar results, in particular \citet{VanErven2015a} and \citet{WicEtAl2019}. Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general. Third, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased. A natural question that arises is what to do in the case of biased reconciled forecasts. Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation. This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.

The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines hierarchical time series in a way that does not depend on any notion of bottom-level series. Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions forf forecast reconciliation.

@@

\begin{figure}[H]
	\begin{center}
		\leaf{AA} \leaf{AB} \leaf{AC}
		\branch{3}{A}
		\leaf{BA} \leaf{BB}
		\branch{2}{B}
		\leaf{CA} \leaf{CB}
		\branch{2}{C}
		\branch{3}{Tot}
		\qobitree
	\end{center}
	\caption{An example of a two level hierarchical structure.}\label{fig:basichier}
\end{figure}

To clarify these concepts, consider the example of the hierarchy in Figure~\ref{fig:basichier}. For this hierarchy, $n=11$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}, y_{CA,t}, y_{CB,t}]'$, $m=7$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}, y_{CA,t}, y_{CB,t}]'$ and
\[
  \bm{S} = \begin{pmatrix}
    1 & 1 & 1 & 1 & 1 & 1 & 1 \\
    1 & 1 & 1 & 0 & 0 & 0 & 0 \\
    0 & 0 & 0 & 1 & 1 & 0 & 0 \\
    0 & 0 & 0 & 0 & 0 & 1 & 1 \\
    & \multicolumn{5}{c}{\bm{I}_7} &
  \end{pmatrix},
\]
where $\bm{I}_7$ is the $7 \times 7$ identity matrix.

While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series. In fact, concepts such as coherence and reconciliation, defined in full below, require the data to have only two important characteristics: the first is that they are multivariate, the second is that they adhere to linear constraints.

@@

\begin{definition}[Coherent subspace]\label{def:cohspace}
   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a some linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
\end{definition}

To further illustrate, Figure~\ref{fig:3D_hierarchy} depicts the simplest three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$. The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space; i.e. $m=2$ and $n=3$. It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$; i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$. In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$. However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$. However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

@@

Although pre-multiplying base forecasts by $\bm{S}\bm{G}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{S}\bm{G}$ has the specific structure of a \emph{projection} matrix onto $\mathfrak{s}$. In general a projection matrix is defined via its idempotence property, i.e. $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$. However we also rely on another property of projection matrices, namely that any vector lying in the image of a projection is mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}. In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{S}\bm{G}\bm{v}=\bm{v}$.

@@

Consider the Euclidean distance between the target and a forecast. This is equivalent to the square root of the sum of squared forecast errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$. The following theorem shows that reconciliation never increases, the sum of squared errors of point forecasts.

@@

However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy. In particular, this measure is the square root of the sum of squared forecast errors of \emph{all} variables in the hierarchy. Consequently, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy. Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT\@. It is to oblique projections that we now turn our attention.

@@

One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the square root of the sum of squared errors of \emph{all} variables in the hierarchy. A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally. For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series. Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating squared errors. An even more sophisticated understanding may take the correlation between series into account. All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix. Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.

@@

Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality). In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality. The proof of \citet{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees. The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$. As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on $\bm{W}$. If Euclidean distance (or mean squared error) is used, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts. This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.

@@

\begin{figure}[!p]
  \centering
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
      \caption{}
  \end{subfigure}
  \caption{A schematic represention of orthogonal and oblique reconciliations. The orange points in (a) represent in-sample errors and $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in (b) indicate potential base forecasts while the blue dot ${\hat{\bm y}}$ represents one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. (c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.}\label{fig:OthogonalVSOblique_projection}
\end{figure}

@@

Before turning our attention to the issue of bias itself it is important to state a desirable property that any reconciliation method should have. That is if base forecasts are already coherent then reconciliation should not change the forecasts. As stated in Section~\ref{sec:Reconciliation}, this property holds only when $\bm{S}\bm{G}$ is a projection matrix. As a corollary, reconciling using an arbitrary $\bm{G}$, may in fact change an already coherent forecast.

@@

The above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$, $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}$ is projected to a point ${\bm{\mu}^*}$ in $\mathfrak{L}$. In this case, the expectation of reconciled forecast will be ${\bm{\mu}^*}$ rather than $\bm{\mu}$ and hence biased.

@@

Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{S}\bm{G}\bm{S}=\bm{S}$ or alternatively that $\bm{G}\bm{S}=\bm{I}$. Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in Appendix A for a proof). However, problems arise when viewing the preservation of unbiasedness through the prism of imposing the constraint $\bm{G}\bm{S}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner. However, equipped with a geometric understanding of the problem, we would advise against this approach. The constraint $\bm{G}\bm{S}=\bm{I}$ is not just about bias. Dropping the constraint compromises all of the attractive properties of projections. It also opens the door to reconciliation methods that change already coherent base forecasts, which suggests an increase in the variability of the forecasts. This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.
